Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-05-10 Moltres.tex
updates acros"

Moltres is an open source code licensed under \gls{LGPL} terms that aims to be a tool that can be
freely used, studied, interrogated, and improved by the \gls{MSR}
community.  Its openness is a defining characteristic and 
promotes unmatched quality through transparency and ease of peer review. In the
era of GitHub\cite{github} and international scientific collaboration, open and modern software practices must be
employed in order for nuclear engineering simulation capability to enable 
discovery and support the regulatory needs presented by new reactor designs. 
Furthermore, to openness is necessary to keep pace with scientific computing 
advances in fields like astronomy whose multitude of open simulation tools
(Enzo, Gadget, Flash, Gizmo, Ramses, Mesa) allows them to be the darlings of
scientific visualization and public interest. In that vein Moltres uses
\mintinline{latex}{git} for version control, integration testing to protect
developed physics capabilities, and a C++ object-oriented design to allow easy
class extensibility and minimal code duplication. Moreover, Moltres is built on
top of the \gls{MOOSE} framework, \cite{gaston_physics-based_2015} another \gls{LGPL}
code that itself leans on LibMesh \cite{kirk2006libmesh}, a \gls{LGPL} finite element
library, and PetSc \cite{petsc-user-ref}, a \gls{BSD}-licensed toolkit for solving nonlinear
equations stemming from discretization of PDEs. \gls{MOOSE} and LibMesh handle
translation of application (Moltres) defined weak PDE forms into residual and
Jacobian functions that are the inputs into PetSc Newton-Raphson solution
routines. All codes use MPI for parallel communication and are easily deployed
on massively-parallel cluster-computing platforms. \gls{MOOSE} applications by default
use monolithic and implicit methods that are ideal for closely-coupled and
multi-scale physics. These methods are ideal for the model problem described in
this work. However, it should be noted that Moltres can also use explicit
time-stepping routines as well as segregated solution methods, making it more
extensible to future problems.

@@

\begin{equation}
%% \frac{1}{v_g}\frac{\partial \phi_g}{\partial t} - \nabla \cdot D_g \nabla \phi_g
%% + \Sigma_g^r \phi_g = \sum_{g \ne g'}^G \Sigma_{g'\rightarrow g}^s \phi_{g'} + \chi_g^p \sum_{g' = 1}^G (1 - \beta)
%% \nu \Sigma_{g'}^f \phi_{g'}
\frac{1}{v_g}\frac{\partial \phi_g}{\partial t} - \nabla \cdot D_g \nabla \phi_g
+ \Sigma_g^r \phi_g = \sum_{g \ne g'}^G \Sigma_{g'\rightarrow g}^s \phi_{g'} + \chi_g^p \sum_{g' = 1}^G (1 - \beta)
\nu \Sigma_{g'}^f \phi_{g'} + \chi_g^d \sum_i^I \lambda_i C_i
\label{eq:neutrons}
\end{equation}

@@

\begin{equation}
\frac{\partial C_i}{\partial t} = \sum_{g'= 1}^G \beta_i \nu \Sigma_{g'}^f
\phi_{g'} - \lambda_i C_i - \frac{\partial}{\partial z} u C_i
\label{eq:precursors}
\end{equation}

@@

Reactor composition is based on the enriched uranium design for the \gls{MSRE}
and is given in \cref{table:comp} \cite{robertson_msre_1965}. Group constants
are generated with either Serpent \cite{leppanen_serpent_2015} or Scale
\cite{dehart_reactor_2011}. Temperature vs group constant interpolation tables
are constructed separately for fuel and moderator regions.

>>>>

Moltres is an open source code licensed under \gls{LGPL} terms that aims to be a tool that can be
freely used, studied, interrogated, and improved by the \gls{MSR}
community.  Its openness is a defining characteristic and 
promotes unmatched quality through transparency and ease of peer review. In the
era of GitHub\cite{github} and international scientific collaboration, open and modern software practices must be
employed in order for nuclear engineering simulation capability to enable 
discovery and support the regulatory needs presented by new reactor designs. 
Furthermore, to openness is necessary to keep pace with scientific computing 
advances in fields like astronomy whose multitude of open simulation tools
(Enzo\cite{enzo}, Gadget\cite{gadget}, Flash\cite{flash}, Gizmo\cite{gizmo}, 
Ramses\cite{ramses}, Mesa\cite{mesa}) allows them to be the darlings of
scientific visualization and public interest.

In that vein, Moltres uses
\mintinline{latex}{git} for version control, integration testing to protect
developed physics capabilities, and a C++ object-oriented design to allow easy
class extensibility and minimal code duplication. Moreover, Moltres is built on
top of the \gls{MOOSE} framework, \cite{gaston_physics-based_2015} another \gls{LGPL}
code that itself leans on LibMesh \cite{kirk2006libmesh}, a \gls{LGPL} finite element
library, and PetSc \cite{petsc-user-ref}, a \gls{BSD}-licensed toolkit for solving nonlinear
equations stemming from discretization of PDEs. \gls{MOOSE} and LibMesh handle
translation of application (Moltres) defined weak PDE forms into residual and
Jacobian functions that are the inputs into PetSc Newton-Raphson solution
routines. All codes use MPI for parallel communication and are easily deployed
on massively-parallel cluster-computing platforms. \gls{MOOSE} applications by default
use monolithic and implicit methods that are ideal for closely-coupled and
multi-scale physics. These methods are ideal for the model problem described in
this work. However, it should be noted that Moltres can also use explicit
time-stepping routines as well as segregated solution methods, making it very 
extensible to myriad future modeling challenges.

\section{Methods}

@@

\begin{align}
%% \frac{1}{v_g}\frac{\partial \phi_g}{\partial t} - \nabla \cdot D_g \nabla \phi_g
%% + \Sigma_g^r \phi_g = \sum_{g \ne g'}^G \Sigma_{g'\rightarrow g}^s \phi_{g'} + \chi_g^p \sum_{g' = 1}^G (1 - \beta)
%% \nu \Sigma_{g'}^f \phi_{g'}
        \frac{1}{v_g}\frac{\partial \phi_g}{\partial t} - \nabla \cdot D_g 
        \nabla \phi_g + \Sigma_g^r \phi_g &= \sum_{g \ne g'}^G 
        \Sigma_{g'\rightarrow g}^s \phi_{g'} + \chi_g^p \sum_{g' = 1}^G (1 - 
        \beta) \nu \Sigma_{g'}^f \phi_{g'} + \chi_g^d \sum_i^I \lambda_i C_i
\label{eq:neutrons}
        \intertext{where}
        <+var+> &= \mbox{<++>} [<+units+>]\\ 
        <+var+> &= \mbox{<++>} [<+units+>]\\ 
        <+var+> &= \mbox{<++>} [<+units+>]\\ 
        <+var+> &= \mbox{<++>} [<+units+>]\\ 
        <+var+> &= \mbox{<++>} [<+units+>]\\ 
        <+var+> &= \mbox{<++>} [<+units+>]\\ 
        <+var+> &= \mbox{<++>} [<+units+>]\\ 
        <+var+> &= \mbox{<++>} [<+units+>]\\ 
        <+var+> &= \mbox{<++>} [<+units+>]\\ 
        <+var+> &= \mbox{<++>} [<+units+>]\\ 
        <+var+> &= \mbox{<++>} [<+units+>]\\ 
        <+var+> &= \mbox{<++>} [<+units+>]\\ 
        <+var+> &= \mbox{<++>} [<+units+>]\\ 
        <+var+> &= \mbox{<++>} [<+units+>]\\ 
        <+var+> &= \mbox{<++>} [<+units+>].
\end{align}

@@

\begin{align}
        \frac{\partial C_i}{\partial t} &= \sum_{g'= 1}^G \beta_i \nu 
        \Sigma_{g'}^f \phi_{g'} - \lambda_i C_i - \frac{\partial}{\partial z} u 
        C_i \label{eq:precursors}
        \intertext{where}
        <+var+> &= \mbox{<++>} [<+units+>]\\ 
        <+var+> &= \mbox{<++>} [<+units+>]\\ 
        <+var+> &= \mbox{<++>} [<+units+>]\\ 
        <+var+> &= \mbox{<++>} [<+units+>]\\ 
        <+var+> &= \mbox{<++>} [<+units+>]\\ 
        <+var+> &= \mbox{<++>} [<+units+>]\\ 
        <+var+> &= \mbox{<++>} [<+units+>]\\ 
\end{align}

@@

Group constants
are generated with either Serpent \cite{leppanen_serpent_2015} or Scale
\cite{dehart_reactor_2011}. Temperature vs group constant interpolation tables
are constructed separately for fuel and moderator regions.

The fuel composition is based on the \gls{BOL} enriched uranium composition in the \gls{MSRE}
and is given in \cref{table:comp} \cite{robertson_msre_1965}.
